A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-05 article/article.tex
start writing embedding chapter.

\subsection{Create subgraphs for coverage analysis}

@@

\subsection{graph embeddings for coverage analysis}

\begin{itemize}
    \item One often utilized strategy in machine learning is to translate raw data like images or text into an embedding space in order to be  
\end{itemize}

@@

This section describes the implementation and application of graph embeddings to traffic scene graphs, as demonstrated in the \texttt{graph\_embeddings.ipynb} notebook. The implementation follows a comprehensive approach to learning graph representations through self-supervised contrastive learning.

\subsection{Graph Neural Network Architecture}

>>>>

\section{Create subgraphs for coverage analysis}

@@

@@

This section describes the concepts, implementation and application of graph embeddings to traffic scene graphs. 
The implementation follows a comprehensive approach to learning graph representations through self-supervised 
contrastive learning.

Embeddings are a widely used method to translate raw data like images or text into an embedding space in order to be 
able to perform machine learning tasks on them. One well known example of this is the Word2Vec model, which is used to 
translate words into a 
vector space, where the distance between vectors can be used to measure the similarity between 
words (\cite{mikolov2013efficientestimationwordrepresentations}).

In the context of traffic scene graphs, embeddings are used to translate the graph structure into a vector space, 
where the distance between vectors can be used to measure the similarity between traffic scenes.
This is useful for coverage analysis, as it allows to compare traffic scenes among each other.
For example, two traffic scenes can be considered similar if the distance between their embeddings is small. This enables
to search for a most similar simulation scenario given a real world scenario, to identify areas with near duplicates or 
to easily visualize structures in the embedding space, which in the original space of all possible traffic scenes
would not be possible.

Graph neural networks (GNNs) are a class of neural networks that are designed to process graph-structured data and have 
gained a lot of popularity in the last years, see for example (add references).

In this paper, a network architecture using a Graph Isomorphism Network with Edge features (GINE) as described 
in \cite{hu2020strategiespretraininggraphneural} is used to generate embeddings for traffic scene graphs as implemented in the 
pytorch geometric library (\cite{Fey/Lenssen/2019}). Main reason for using this specific architecture is that is capable of
learning embedding representations not only on the graph structure itself but on both node and edge attributes. Other 
network architectures like GraphSAGE or GAT are not capable of this. (TODO: check if this is true)
